\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png} \\ {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-5mm}

### 2024-01-19 text/paper/paper.tex
Friday, 19 January 2024 at 17:45:23
MEEEERDA

There are three noticeable structures in this spectrum. 
The first one is a peak around 0 keV, which is just electronic noise. The following structure is backscattering, identified by the barrier of 1146.5 kEv. 
The backscattering is followed by event pile-up, which is the energy profile referenced in section \ref{sec:energy_profile_peak}.

>>>>

There are three noticeable structures in this spectrum. 
The first one is a peak around 0 keV, which is just electronic noise. The following structure is backscattering, identified by the barrier of 1146.5 kEv. 
The backscattering is followed by event pile-up, which happens whenever two particles are detected at the same time and the detector only detects one with the energy doubled.
The last structure is the lithium peak. The depth of the sample creates the visible energy profile and this procedure is explained in section \ref{sec:energy_profile_peak}.
